\documentclass{article}

% TODO
% - change font, especially for italics
% - add TA roles

\input{style}

\renewcommand{\maketitle}{
\begin{center}
  {\large{Benjamin~~Lee~~Greenman}}
\vspace{0.1cm}
\\Brown University
\\CIT building
\\115 Waterman St
\\Providence RI 02912
% \\Northeastern University
% \\308 West Village H
% \\440 Huntington Avenue
% \\Boston MA 02115
\\\texttt{benjamin.l.greenman\,@\,gmail.com}
\\\texttt{781-924-9989}
\end{center}
}

\begin{document}

\maketitle

%% \mysection{Contact}

\mysection{Research Interests}

Migratory Typing,~~Language Design,~~Type Theory,~~Constructions

\mysection{Education}
\begin{itemize}
\item {Hudson Valley Community College} \hfill \datespan{2009}{2010}\\
\begin{tabular}{>{\it}r l}
General Studies & \\
\end{tabular}

\item {Cornell University} \hfill \datespan{2010}{2013}\\
\begin{tabular}{>{\it}r l}
Degree & Bachelor of Science\\
Major & Industrial and Labor Relations\\
Minor & Computer Science\\
\end{tabular}

\item {Cornell University} \hfill \datespan{2013}{2014}\\
\begin{tabular}{>{\it}r l}
Degree & Master of Engineering\\
Major & Computer Science\\
Advisor & \href{http://www.cs.cornell.edu/~ross/}{Ross Tate}
\end{tabular}

\item {Northeastern University} \hfill \datespan{2014}{2020}\\
\begin{tabular}{>{\it}r l}
Degree & Ph.D \\
Area & Programming Languages \\
Advisor & \href{http://ccs.neu.edu/home/matthias}{Matthias Felleisen} \\
Thesis & \href{http://ccs.neu.edu/home/types/resources/pdf/g-dissertation-2020.pdf}{Deep and Shallow Types}
\end{tabular}
\end{itemize}


\mysection{Employment}
\begin{itemize}
\item {Rentenna Inc.} \hfill \datespan{2012}{2014}\\
  Software Engineering Intern

\item {Cornell University} \hfill \datespan{2012}{2014}\\
  Research Assistant

\item {Knightsbridge Park} \hfill 2017 \\
  Consultant, Web Scraping

\item {Brown University} \hfill \datespan{2021}{ongoing} \\
  Postdoctoral Researcher, \href{https://cifellows2020.org/}{CIFellows 2020}

\end{itemize}


\mysection{Teaching}
\begin{itemize}
  \item \tainfo{TA}{\href{http://www.cs.cornell.edu/courses/cs3110/2012sp/}{Functional Programming and Data Structures}}{\datespan{2012}{2014}}
  \item \tainfo{TA}{\href{https://course.ccs.neu.edu/cs3500sp16/}{Object-Oriented Design}}{2016}
  \item \tainfo{TA}{\href{https://course.ccs.neu.edu/cs2500f16/}{Fundamentals I (Computing and Programming)}}{2016}
  \item \tainfo{TA}{\href{http://www.ccs.neu.edu/home/matthias/4500-f18/index.html}{Software Development}}{2018, 2020}
  \item \tainfo{Organizer}{\href{http://cs.brown.edu/courses/csci2950-x/2021/}{Topics in PL and Systems: Tables and Humans}}{2020}
\end{itemize}


\mysection{Students Supervised}
%% Name , Degree , Institution , Year(s)

\begin{itemize}
  \item \stinfo{Zeina Migeed}{B.S.}{Northeastern University}{\datespan{2016}{2017}}
  \item \stinfo{Milo Davis}{B.S.}{Northeastern University}{2017}
  \item \stinfo{Kuang-Chen Lu}{Ph.D.}{Brown University}{\datespan{2020}{ongoing}}
  \item \stinfo{Quianfan Chen}{B.S.}{Brown University}{\datespan{2020}{ongoing}}
\end{itemize}


\mysection{Awards} %% \& Grants
\begin{itemize}
  \item {Cornell Computer Science Teaching Award} \hfill 2013
  \item {Cornell Computer Science Teaching Award} \hfill 2014
  \item {Northeastern CCIS Graduate Community Service Award} \hfill 2016
  \item \href{https://cifellows2020.org}{{CRA/CCC/NSF CI Fellowship}} \hfill \datespan{2021}{ongoing}
\end{itemize}


\mysection{Service}
\begin{itemize}
  \item {CCIS Social Hour Czar} \hfill {\datespan{Fall 2014}{Spring 2017}}
  \item {Student Volunteer} \hfill \href{http://2015.ecoop.org/}{ECOOP 2015}
  \item {Student Volunteer} \hfill \href{http://icfpconference.org/icfp2015/}{ICFP 2015}
  \item {PRL Webmaster} \hfill \href{https://github.com/nuprl/website}{\datespan{Fall 2016}{Fall 2018}}
  \item {GTP Webmaster} \hfill \href{https://github.com/nuprl/gtp.github.io}{\datespan{Spring 2016}{Spring 2019}}
  \item {Student Volunteer} \hfill \href{http://conf.researchr.org/home/POPL-2016}{POPL 2016}
  \item {Student Volunteer} \hfill \href{http://conf.researchr.org/home/PLDI-2016}{PLDI 2016}
  \item {Student Volunteer} \hfill \href{http://2016.ecoop.org/}{ECOOP 2016}
  \item {Artifact Evaluation Committee} \hfill \href{http://2016.splashcon.org/track/splash-2016-artifacts}{OOPSLA 2016}
  \item {Student Volunteer} \hfill \href{https://www.acm.org/turing-award-50/conference}{Turing Celebration 2017}
  \item {Artifact Evaluation Committee} \hfill \href{https://2017.ecoop.org/track/ecoop-2017-Artifacts}{ECOOP 2017}
  \item {Artifact Evaluation Committee} \hfill \href{https://2017.splashcon.org/track/splash-2017-OOPSLA-Artifacts}{OOPSLA 2017}
  \item {Student Volunteer} \hfill \href{http://conf.researchr.org/home/POPL-2018}{POPL 2018}
  \item {CCIS Hiring Committee student representative} \hfill {Spring 2018}
  \item {Student Volunteer (Slack Monitor)} \hfill \href{https://icfp18.sigplan.org/committee/icfp-2018-organizing-committee}{ICFP 2018}
  \item {Housing Chair} \hfill \href{https://2018.splashcon.org/committee/splash-2018-organizing-committee}{SPLASH 2018}
  \item {PRL Coffee Czar} \hfill {Fall 2019 -- Spring 2020}
  \item {Student Volunteer} \hfill \href{https://2019.splashcon.org/}{SPLASH 2019}
  \item {PRL Offsite Organizer} with \href{https://www.khoury.northeastern.edu/people/olek-gierczak/}{Olek Gierczak} and \href{http://ccs.neu.edu/home/amal/}{Amal Ahmed} \hfill {Fall 2019}
  \item {Reviewer} \hfill \href{https://www.cambridge.org/core/news/jfp-special-issue-on-gradual-typing}{JFP Special Issue on Gradual Typing}
  \item {Program Committee} \hfill \href{https://pldi21.sigplan.org/committee/pldi-2021-papers-program-committee}{PLDI 2021}
  \item {Program Committee} \hfill \href{https://icfp21.sigplan.org/committee/icfp-2021-papers-program-committee}{ICFP 2021}
\end{itemize}

% declined PC: OOPSLA 2022, PLDI 2020
% declined minor PC: HATRA 2021, DLS 2021


\mysection{Publications}

\mysubsection{Journal}
\begin{itemize}
\item
  Ben Greenman, Asumu Takikawa, Max S. New, Daniel Feltey, Robert Bruce Findler, \hfill JFP 2019 \\
  Jan Vitek, and Matthias Felleisen. \\
  \emph{How to Evaluate the Performance of Gradual Type Systems} \\
  Cambridge, United Kingdom.
\item
  Ben Greenman, Lukas Lazarek, Christos Dimoulas, and Matthias Felleisen \hfill Programming 2022 \\
  \emph{A Transient Semantics for Typed Racket} \\
  Porto, Portugal.
\item
  Kuang-Chen Lu, Ben Greenman, and Shriram Krishnamurthi \hfill Programming 2022 \\
  \emph{Types for Tables: A Language Design Benchmark} \\
  Porto, Portugal.
\end{itemize}

\mysubsection{Conference and Symposium}
\begin{itemize}
\item
  Ben Greenman, Fabian Muehlboeck, and Ross Tate. \hfill PLDI 2014 \\
  \emph{Getting F-Bounded Polymorphism into Shape}. \\
  Edinburgh, Scotland.
\item
  Asumu Takikawa, Daniel Feltey, Ben Greenman, Max S. New, Jan Vitek, \hfill POPL 2016 \\
   and Matthias Felleisen. \\
   \emph{Is Sound Gradual Typing Dead?} \\
  St. Petersburg, Florida.
\item
  Stephen Chang, Ben Greenman, and Alex Knauth. \hfill POPL 2017 \\
   \emph{Type Systems as Macros} \\
  Paris, France.
\item
  Sam Tobin-Hochstadt, Matthias Felleisen, Robert Bruce Findler, Matthew Flatt, \hfill SNAPL 2017 \\
  Ben Greenman, Andrew M. Kent, Vincent St-Amour, T. Stephen Strickland, \\
  and Asumu Takikawa. \\
  \emph{Migratory Typing: 10 Years Later} \\
  Monterey, California.
\item
  Ben Greenman, Zeina Migeed. \hfill PEPM 2018 \\
  \emph{On the Cost of Type-Tag Soundness} \\
  Los Angeles, California.
\item
  Ben Greenman, Matthias Felleisen. \hfill ICFP 2018 \\
  \emph{A Spectrum of Type Soundness and Performance} \\
  St. Louis, Missouri.
\item
  Daniel Feltey, Ben Greenman, Christophe Scholliers, Robert Bruce Findler, \hfill OOPSLA 2018 \\
  and Vincent St. Amour. \\
  \emph{Collapsible Contracts: Fixing a Pathology of Gradual Typing} \\
  Boston, Massachusetts.
\item
  Preston Tunnell Wilson, Ben Greenman, Justin Pombrio, Shriram Krishnamurthi. \hfill DLS 2018 \\
  \emph{The Behavior of Gradual Types: A User Study} \\
  Boston, Massachusetts.
\item
  Ben Greenman, Matthias Felleisen, and Christos Dimoulas \hfill OOPSLA 2019 \\
  \emph{Complete Monitors for Gradual Types} \\
  Athens, Greece.
\item
  Lukas Lazarek, Ben Greenman, Matthias Felleisen, and Christos Dimoulas \hfill ICFP 2021 \\
  \emph{How to Evaluate Blame for Gradual Types} \\
  Virtual / Airmeet.
\end{itemize}

\mysubsection{Workshop}
\begin{itemize}
\item
  Asumu Takikawa, Daniel Feltey, Ben Greenman, Max S. New, Jan Vitek, \hfill STOP 2015 \\
   and Matthias Felleisen. \\
   \emph{Position Paper: Performance Evaluation for Gradual Typing}. \\
  Prague, Czech Republic.
\end{itemize}


\mysection{Invited Talks}
\begin{itemize}
  \item
    \href{https://2018.splashcon.org/track/grace-2018-papers}{GRACE Workshop} \hfill 2018\\
    \emph{Three Approaches to Gradual Typing}.
  \item
    \href{https://www.bu.edu/cs/research/popv/seminar/}{BU POPV Seminar} \hfill {2020}\\
    \emph{Complete Monitoring for Gradual Types}.
  \item
    \href{https://con.racket-lang.org/2020}{Racket Con} \hfill 2020\\
    \emph{Shallow Typed Racket}.
\end{itemize}


\mysection{Achievements}

\begin{itemize}
  \item 35 video game world records \href{https://www.twingalaxies.com/scores.php?player=43761}{[link]} \hfill \datespan{2007}{2008}
  \item 3rd~place Pennsylvania State Birling Championship \hfill 2013, 2014
  \item 2nd~place Pennsylvania State Birling Championship \hfill 2016, 2017
  \item 1st~place Pennsylvania State Birling Championship \hfill 2018, 2019
  \item 2nd~place Barkpeelers Greased Pole Competition \hfill 2015, 2018
  \item Barkpeelers Grand Champion (tied with Ben Barner) \href{http://lumbermuseum.org/bark-peeler-festival/festival-events-2019/bark-peeler-festival-2018/}{[link]} \hfill 2018
\end{itemize}

\end{document}
