\documentstyle[hyperref, margin, line]{resume}
\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}
\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\textsc}

%% Macros
\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}

\begin{document}

\name{B~e~n~j~a~m~i~n~~~L~e~e~~~G~r~e~e~n~m~a~n}
\address{
phone: 936.666.1126 \hspace{0.5cm}
email: blg59@cs.cornell.edu
}

\begin{resume}

%% \vspace{0.5cm}

\section{\textsc{Education}}

\textbf{Cornell University} \hfill 2013 \textendash 2014 \\
Master of Engineering, Computer Science, GPA 3.52

\textbf{Cornell University} \hfill 2010 \textendash 2013\\
Bachelor of Science, GPA 3.47%%. Computer Science GPA 3.76

\textbf{Hudson Valley Community College} \hfill 2009 \textendash 2010 \\ 
GPA 3.78\\
Phi Theta Kappa National Honor Society


\begin{formatb}
  \employer{l}\title{r}\\
  \location{l}\dates{r}\\
  \body\\
\end{formatb}

\vfill
%% \vspace{0.70cm}

\section{\textsc{Experience}}

\employer{\textbf{Research Assistant, Cornell University}}
\title{Summer 2013 \textendash \ Fall 2014}
\location{}
\dates{Ithaca, NY}
\begin{position}
(\emph{Summer 2013} \textendash \emph{Summer 2014})  Worked with Professor Ross Tate to determine the feasibility of a new construct for object-oriented languages.
Analyzed the inheritance hierarchy of over 13 million of lines of Java code across 60 open source projects to analyze existing practice and assess the work needed to implement the redesign.
Presented findings at PLDI '14.
\\
(\emph{Summer 2014} \textendash \emph{Fall 2014})  Building on the previous work, designed a type system for adding conditional inheritance to object-oriented languages with generics.
Overcame challenges of decidability and soundness to create a practical, language-independent formalism.
\end{position}

\employer{\textbf{Software Engineer, Rentenna Inc.}}
\title{Summer 2012 \textendash Winter 2013}
\location{}
\dates{New York, NY}
\begin{position}
Implemented \textsc{rest-}ful api for growing startup.
Wrote an extensive library of \textsc{html} and \textsc{xml} crawlers.
Designed caching abstraction to enrich local database with dynamic external resources.
Published user-facing web page features and modules.
Gained experience with unit-testing frameworks and a branching Git model.
\end{position}

\employer{\textbf{Teaching Assistant, Cornell University}}
\title{Spring 2012 \textendash Spring 2014}
\location{}
\dates{Ithaca, NY}
\begin{position}
Introduced undergraduate students to functional programming.
Designed assignments and exam questions. 
Wrote a test harness in the OCaml language to automate grading.
Interacted extensively with students in one-on-one and classroom settings.
Helped manage a staff of approximately 20 teaching assistants.
\end{position}

%% \employer{\textbf{Ithaca Media Arts}}
%% \title{Camp Counselor}
%% \location{Ithaca, NY}
%% \dates{Summer 2011 \textendash\ Spring 2012}
%% \begin{position}
%% Ran LEGO Mindstorms camp for K-12 children. 
%% Held daily camps in the summer and weekly camps during the school year. 
%% Made accomodations for children with ADHD and autism.
%% \end{position}

%% \employer{\textbf{Cooperative Cleaning Services}}
%% \title{Custodian}
%% \location{Ithaca, NY}
%% \dates{Fall 2010 \textendash\ Spring 2012}
%% \begin{position}
%% Helped owner manage and expand small business
%% Worked in a variety of commercial and industrial settings. 
%% Communicated with building managers on a daily basis. 
%% Trained 4 new employees. 
%% \end{position}\\

%% \employer{\textbf{Garcias Tacqueria}}
%% \title{Kitchen Supervisor}
%% \location{Delmar, NY}
%% \dates{Spring 2007 \textendash\ Fall 2009}
%% \begin{position}
%% Synchronized work schedule, recruited and interviewed new employees
%% \end{position}

\vfill
%% \vspace{1.00cm}

\renewcommand*\arraystretch{1.2}
\section{\textsc{Coursework}}
\begin{tabular}{lllll}
 Operating Systems      & \ \ & Programming Languages           & \ \ & Computer Organization \\
 Algorithm Design      & \ \ & Organizational Behavior       & \ \ & Abstract Algebra    \\
 Information Networks     & \ \ & Functional Data Structures       & \ \ &  Entrepreneurship       \\
 Compilers      & \ \ &  Policy Analysis   & \ \ & Object-Oriented Design   \\
\end{tabular}\\

%% \section{\textsc{Publications}}

%% \textbf{Getting F-Bounded Polymorphism Back Into Shape} \hfill to appear in PLDI 2014\\
%% Benjamin Lee Greenman, Fabian Muelboeck, Ross Tate

\vfill
%% \vspace{1.00cm}

\section{\textsc{Qualifications}}

\textbf{Awards}: Cornell Teaching Award, 2014 \& 2013

\textbf{Programming Languages}: Python, OCaml, SQL, Coffeescript, Sass, Java, Haskell

\textbf{Libraries and Tools}: Emacs, GIMP, Git, \LaTeX, MongoDB, Scrapy, SQLAlchemy, XPath

\textbf{Other}: 35 video game world records, 3\third \ place Pennsylvania State Birling championship

\vfill{}

\end{resume}
\end{document}
